---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statgl

Query and visualize data published by Statistics Greenland.

## Installation

You can install the development version of statgl from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("StatisticsGreenland/statgl")
```

To load the package contents to the R environment, run:

```{r}
library(statgl)
```

## Search

Use `statgl_search` to do a freetext search of the Greenland Statbank:

```{r}
statgl_search("population jan* 1st")
```

## Fetch

The ID's found in search results are unique table ID's, which can be collected by `statgl_fetch`:

```{r}
statgl_fetch("BEESTA")
```

Eliminable variables are removed by default. To see which variables can be queried, use `statgl_meta`:

```{r}
statgl_meta("BEESTA")
```

Codes from `values` columns can be used to query:

```{r}
statgl_fetch("BEESTA", gender = c("M", "K"), age = 0:99)
```

Use `.eliminate_rest = FALSE` to show all values of remaining eliminables:

```{r}
statgl_fetch("BEXSTA", .eliminate_rest = FALSE)
```

## ggplot

The package comes with extensions for ggplot2, to create data visualizations following the Statistics Greenland design manual:

```{r}
library(ggplot2)

ggplot(statgl_fetch("BEESTA", gender = c("M", "K"))) +
  geom_line(aes(as.numeric(time), value, color = gender)) +
  scale_color_statgl() +
  theme_statgl()
```

